\documentclass[a4paper]{report}
\pagestyle{headings}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\lstset{language=bash}
\lstset{numbers=right}
\lstset{breaklines}
\title{Lab Report for Object-oriented Programming course \newline
 Lab 4: Big Integer Matrix}
\author{Wang, Chen \\ 16307110064 \\ School of Software\\ Fudan University}
\date{\today}
\bibliographystyle{plain}
\begin{document}
\maketitle

\tableofcontents

\chapter{Requirements of this Lab \& Functions of this application}
In this lab, we are required to realize a matrix supporting big integers that that utilizes the operator overloading function in C++.
\par
More specifically, the application we designed should satisfy the characteristics in the following sections.
\section{Operator overloading and implementation}
We need to implement a 3 by 3 matrix class that supports large numbers and overload the following operators:
\par
+: Add two matrices
\par
-: subtraction of two matrices
\par 
*: Multiply two matrices (e.g: A*B)
\par
*: Multiply a constant by a matrix (e.g. 3*A)
\par
\textasciitilde : Transpose of a matrix
\section{Expression evaluation}
The application should support for compound expressions (without parentheses). Such as: A+B-C, A+B*C, A+B+=C, etc.
\section{Operator priority handling}
We need to consider the operator priority.
\par
Priority: \textasciitilde \textgreater * \textgreater +, -
\chapter{Task completion in my application}
My hand in version of the application accomplishes all the requirements above.
\par
The implementation ideas can be found from the clear comments of the source code.
\section{General implementation ideas of the application}
\subsection{The big integer class}
The big integer class that is used to represent a big integer and to
perform calculations on big integers.
\par
The big integers are stored as a string and the size of the big integer
is restricted by the length of the string allowed on the specific operating
system. On modern 64 bit operating systems, the length allowed to a string
is approximately 2 billion.
\par
The operators supported by this class are add, subtract and multiply.
However, some other manipulations are currently realized for the sake of
internal usage. The three operators are overloading the system operators
+, -, and * separately.
\par
The constructor of this class allows string argument only. However, for
the sake of copy constructors, an empty constructor is also designed.
\par
@author Wang, Chen
\par
@class bigInteger
\par
@date June 4th, 2019

\subsection{The matrix class}
The matrix class is designed to represent a 3 by 3 matrix whose
elements are big integers. The big integer implementation relies
on the big integer class in this project. The maximal length of the
big integers depend on the length allowed for the strings on a system
The matrix class support the same operations as the big integers.
\par
The operators supported by this class are add, subtract and multiply.
However, some other manipulations are currently realized for the sake of
internal usage. The three operators are overloading the system operators
+, -, and * separately.
\par
It should be noted that * operator has two different functions. They are
matrix multiply matrix and big integer multiply matrix separately.
\par
The constructor of this class allows string array argument only. However, for
the sake of copy constructors, an empty constructor is also designed.
\par
@author Wang, Chen
\par
@class matrix
\par
@date June 4th, 2019

\section{The interfaces of operation}
\subsection{The Matrix object}
\begin{lstlisting}[language=C++]
matrix() = default;
~matrix() = default;
explicit matrix(std::string matrix[]);
friend const matrix operator+(matrix &left, matrix &right);
friend const matrix operator-(const matrix &left, const matrix &right);
friend const matrix operator*(const matrix &left, const matrix &right);
friend const matrix operator*(const bigInteger &bigNum, const matrix &right);
friend const matrix operator~(const matrix &right);
friend matrix &operator+=(matrix &left, const matrix &right);
friend matrix &operator-=(matrix &left, const matrix &right);
friend std::ostream &operator<<(std::ostream &stream, const matrix &matrix1);
\end{lstlisting}

\subsection{The big integer object}

\begin{lstlisting}[language=C++]
bigInteger() = default;
explicit bigInteger(std::string number);
bigInteger &operator+=(const bigInteger &other);
friend bigInteger operator+(bigInteger b1, const bigInteger &b2);
friend bigInteger operator-(bigInteger b1, const bigInteger &b2);
friend bigInteger operator*(bigInteger b1, const bigInteger &b2);
friend std::ostream &operator<<(std::ostream &os, const bigInteger &num);
friend bool operator==(bigInteger b1, const bigInteger &b2);
\end{lstlisting}


\chapter{Correctness validation for my application}
My application correctly handles the following expressions below, which are from the Teaching Assistance's public result validation methods. 
The validation expressions and test results are attached along with the documentation.
\chapter{Platform specification}
This application runs well on Windows systems. Below are the specifications of the running platform and compiling environment. Nevertheless, this application should be able to run on a wider range of platforms other than the one specified below.
\section{Windows Platform}
\subsection{Compiling environments}
\begin{enumerate}
\item
\textbf{Environment:} MinGW version 5.2
\item
\textbf{CMake:} JetBrains CLion bundled CMake version 3.14.4
\item
\textbf{CMake C++ Standard} 17
\end{enumerate}
\subsection{System environments}
[System Summary]
\par
Item	Value	
\par
OS Name	Microsoft Windows 10 Pro	
\par
Version	10.0.17763 Build 17763	
\par
Other OS Description 	Not Available	
\par
OS Manufacturer	Microsoft Corporation	
\par
System Name	DESKTOP-QNL9V7R	
\par
System Manufacturer	LENOVO	
\par
System Model	80W0	
\par
System Type	x64-based PC	
\par
System SKU	LENOVO\_MT\_80W0\_BU\_idea\_FM\_Lenovo XiaoXin Air 13 Pro	
\par
Processor	Intel(R) Core(TM) i7-6500U CPU @ 2.50GHz, 2601 Mhz, 2 Core(s), 4 Logical Processor(s)	
\par
BIOS Version/Date	LENOVO 3GCN24WW(V2.05X), 3/8/2018	
\par
SMBIOS Version	2.8	
\par
Embedded Controller Version	2.24	
\par
BIOS Mode	UEFI	
\par
BaseBoard Manufacturer	LENOVO	
\par
BaseBoard Product	Lenovo XiaoXin A	
\par
BaseBoard Version	SDK0K09938 WIN	
\par
Platform Role	Mobile	
\par
Secure Boot State	Off	
\par
PCR7 Configuration	Elevation Required to View	
\par
Windows Directory	C:$\backslash$Windows	
\par
System Directory	C:$\backslash$Windows$\backslash$system32	
\par
Boot Device	$\backslash$Device$\backslash$HarddiskVolume1	
\par
Locale	 China	
\par 
Hardware Abstraction Layer	Version = "10.0.17763.503"	
\par
User Name	DESKTOP-QNL9V7R$\backslash$zhang	
\par
Time Zone	China Standard Time	
\par
Installed Physical Memory (RAM)	8.00 GB	
\par
Total Physical Memory	7.85 GB	
\par
Available Physical Memory	1.39 GB	
\par
Total Virtual Memory	10.5 GB	
\par
Available Virtual Memory	1.26 GB	
\par
Page File Space	2.60 GB	
\par
Page File	C:$\backslash$pagefile.sys	
\par
Kernel DMA Protection	Off	
\par
Virtualization-based security	Running	
\par
Virtualization-based security Required Security Properties		
\par
Virtualization-based security Available Security Properties	 Base Virtualization Support, DMA Protection
\par	
Virtualization-based security Services Configured	Hypervisor enforced Code Integrity	
\par
Virtualization-based security Services Running	Hypervisor enforced Code Integrity	
\par
Device Encryption Support	Elevation Required to View	
\par

\end{document} 